Plume-SPH 1.0: A 3D dust-gas volcano plume model based on smoothed particle hydrodynamics

### 2016-12-29 Manuscripts_GMD.tex
update the strong scalability tests

All of these existing 3D models are based on mesh based methods (Eulerian methods). And there is no 3D plume model based on mesh free method (Lagrange methods) yet. Actually, Lagrangian methods have several features that are suitable for volcano plume simulation. Among such Lagrangian methods, Smoothed Particle Hydrodynamics \citep{gingold1977smoothed,lucy1977numerical}, even though relatively newer compared to well designed mesh based methods such as Finite Difference, has shown good agreement with experiments by many applications in fluid dynamic area. And it currently is, by far the most widely used scheme. Implementations of SPH in volcanology are keeping showing up \citep{bursik2003smoothed,herault2010sph,haddad2016smoothed}.\\

>>>>

All of these existing 3D models are based on mesh based methods (Eulerian methods). And there is no 3D plume model based on mesh free method (Lagrange methods) yet. Actually, Lagrangian methods have several features that are suitable for volcano plume simulation. Among such Lagrangian methods, Smoothed Particle Hydrodynamics \citep{gingold1977smoothed,lucy1977numerical}, even though relatively newer compared to well designed mesh based methods such as Finite Difference, has shown good agreement with experiments by many applications in fluid dynamic area. And it currently is, by far the most widely used scheme. The first implementations of SPH in volcanology was presented by \citep{bursik2003smoothed} and afterwards, more implementations of SPH in volcanology \citep{mcdougall2004model,
herault2010sph, prakash2011three,bilotta2015gpusph, haddad2016smoothed} has been keeping showing up. All of these implementations are for imcompressible or weakly compressible on-ground flow.\\
